Effects of bariatric surger and weight loss on resting-state functional connectivity

### 2020-12-03 manuscript/draft_rsfmri.Rmd
fix working directory

```{r "environment setup", include=FALSE}

# load packages
library(car) # version 3.0.9
library(plyr) # version 1.8.6
library(dplyr) # version 1.0.2
library(tidyr) # version 1.1.2
library(kableExtra) # version 1.2.1
library(ggplot2) # version 3.3.2
library(patchwork) # version 1.0.1; API for sequentially building up a plot (similar to gridExtra and cowplot)
#library(cowplot)
library(RColorBrewer) # version 1.1.2
library(psych) # version 2.0.8
#library(lsr) 
#library(wesanderson) # colour palette
#library(haven)

library(knitr) # version 1.30
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE) # fig.height=2, fig.width=4)
options(knitr.table.format = "latex") 
# put the path to this file here (working directory for Rmarkdown):
opts_knit$set(root.dir = getwd())
```
# Abstract

# Introduction

>>>>

```{r "load packages", include=FALSE}

# load packages
library(car) # version 3.0.9
library(plyr) # version 1.8.6
library(dplyr) # version 1.0.2
library(tidyr) # version 1.1.2
library(kableExtra) # version 1.2.1
library(ggplot2) # version 3.3.2
library(patchwork) # version 1.0.1; API for sequentially building up a plot (similar to gridExtra and cowplot)
#library(cowplot)
library(RColorBrewer) # version 1.1.2
library(psych) # version 2.0.8
#library(lsr) 
#library(wesanderson) # colour palette
#library(haven)
library(knitr) # version 1.30
```

```{r "knit setup"}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE) # fig.height=2, fig.width=4)
options(knitr.table.format = "latex") 
# set working directory of knit (RMarkdown) to directory of Rproj
opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
setwd(knitr::opts_knit$get("root.dir"))
```
